Reliable error estimation for Sobol' indices\thanks{This work is supported by the CITiES project funded by the Agence Nationale de la Recherche (grant ANR-12-MONU-0020) and by the United States National Science Foundation (grant DMS-1522687).}

### 2017-02-20 article_review/Manuscript.tex
added Section 5.3, reworked Section 5.2, deleted c_j figures

Then, as an alternative to the common Sobol' indices estimators (\ref{common.sobol.est}), we can define the following two estimators with their respective error bounds:
\begin{gather}
\begin{aligned}
\widehat{\underline{S}}_u & = \frac{1}{2}\left(\min\Big{(}\max_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \underline{S}_u(\vI),1\Big{)} + \max\Big{(}\min_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \underline{S}_u(\vI),0\Big{)} \right) \\
\varepsilon_{\widehat{\underline{S}}_u} & = \frac{1}{2}\left(\min\Big{(}\max_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \underline{S}_u(\vI),1\Big{)} - \max\Big{(}\min_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \underline{S}_u(\vI),0\Big{)} \right)
\end{aligned}
\label{formula_undersu}
\end{gather}
and,
\begin{gather}
\begin{aligned}
\widehat{\overline{S}}_u & = \frac{1}{2}\left(\min\Big{(}\max_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \overline{S}_u(\vI),1\Big{)} + \max\Big{(}\min_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \overline{S}_u(\vI),0\Big{)} \right) \\
\varepsilon_{\widehat{\overline{S}}_u} & = \frac{1}{2}\left(\min\Big{(}\max_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \overline{S}_u(\vI),1\Big{)} - \max\Big{(}\min_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \overline{S}_u(\vI),0\Big{)} \right)
\end{aligned}
\label{formula_oversu}
\end{gather}
Because numerator and denominator are both known to be positive, maximizing $\underline{S}_u(\vI)$ (resp. $\overline{S}_u(\vI)$) is done through maximizing the numerator $I_1$ (resp. $I_2$) and minimizing the denominator $I_3-I_4^2$. Analogously, to minimize $\underline{S}_u(\vI)$ (resp. $\overline{S}_u(\vI)$) one minimizes the numerator $I_1$ (resp. $I_2$) and maximizes the denominator $I_3-I_4^2$. As an example, Figure \ref{fig:1} illustrates the region of possible values of $\underline{S}_2(\vI)$ given the true value of $I_1$ for the test function of Bratley \textit{et al.} \cite{Bratley}. This function is further described in Section \ref{sec:5}. 
\begin{figure}[!ht]
\caption{The delimited region on the figure represents the values $\underline{S}_2$ in $\vI\in B_{(0,0,0.05,0.1)}(\widehat{\vI})$ for the Bratley \textit{et al.} function. There, $\underline{S}_2^{\min}=\max\Big{(}\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_2(\vI),0\Big{)}$ and $\underline{S}_2^{\max}=\min\Big{(}\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_2(\vI),1\Big{)}$, and $\widehat{\underline{S}}_2=(\underline{S}_2^{\min}+\underline{S}_2^{\max})/2$.}
\centering
\includegraphics[width=.5\textwidth]{estimator_3d_small.eps}
\label{fig:1}       % Give a unique label
\end{figure}

@@

If the stopping criterion is satisfied, the algorithm stops and Sobol' estimates are returned. Otherwise, $m$ is incremented by one to perform a new estimation. 
\begin{algorithm}[!ht]
\caption{Sequential estimation of Sobol' indices}
\begin{algorithmic}[1]
\vspace*{0.2cm}
\State choose $\epsilon >0$
\State set: $m \leftarrow \ell_*+r$
\State $bool \leftarrow false$
\While {$! bool$}
\State $\mathcal{P}_m \leftarrow \mathcal{P}_{m-1} \cup B_m$

@@

Assume that the number of small first-order indices is known and equals $\gamma$. We denote by $u_1,\dots,u_{\gamma}$ the indices of the corresponding inputs and $\Gamma = \{1,\dots,\gamma\}$. The cost of Variant $A$ including ``Correlation 2" becomes, 
\begin{equation}
\sum \limits_{j \in \Gamma} 2^{m''_{u_j}} + \sum \limits_{j \in \Gamma} 2^{m'_{u_j}} + \sum \limits_{j \in \mathcal{D}\setminus{\Gamma}} 2^{m_{u_j}} + 2 \times 2^{m^\star},
\label{cost.improvement}
\end{equation}
where: %$m'_{u_j}\leq m^{\star}$, $\ m_{u_j} \leq m^{\star}$, and: 
\begin{itemize}
\item[$\bullet$] for $j\in \Gamma$, $2^{m''_{u_j}}$ is the number of evaluations \\ $f\left(\vz_{i,u_j}:\vx_{i,-u_j}\right)$ to estimate $\underline{S}_{u_j}$,
\item[$\bullet$] for $j\in \Gamma$, $2^{m'_{u_j}}$ is the number of evaluations \\ $f\left(\vx_{i,u_j}:{\vx'}_{i,-u_j}\right)$ to estimate both $\underline{S}_{u_j}$ and  $\overline{S}_{u_j}$,
\item[$\bullet$] likewise, for $j\in \mathcal{D}\setminus{\Gamma}$, $ 2^{m_{u_j}}$ is the number of evaluations $f\left(\vx_{i,u_j}:{\vx'}_{i,-u_j}\right)$ to estimate both $\underline{S}_{u_j}$ and  $\overline{S}_{u_j}$,
\item[$\bullet$] $2 \times 2^{m^{\star}}$ is the number of evaluations $f\left(\vx_{i}\right)$ and $f\left({\vx'}_{i}\right)$ used in the estimation of each first-order and total effect index.
\end{itemize}
We recall the cost of Variant $A$ without  ``Correlation 2",
\begin{equation}
\sum \limits_{j \in \Gamma} 2^{m_{u_j}} + \sum \limits_{j \in \mathcal{D}\setminus{\Gamma}} 2^{m_{u_j}} + 2 \times 2^{m^{\star}}. 
%\qquad m_{u_j} \leq m^{\star}.
\label{cost.non.improvement}
\end{equation}
The difference (\ref{cost.improvement}) $-$ (\ref{cost.non.improvement}) equals:
\begin{equation}
 \sum \limits_{j \in \Gamma} 2^{m_{u_j}} \left(2^{m''_{u_j}-m_{u_j}}  + 2^{m'_{u_j}-m_{u_j}} - 1 \right) = \sum \limits_{j \in \Gamma} c_j.
\label{cost.comparison}
\end{equation}
{\color{purple} (Lolo) The sign of \eqref{cost.comparison}} indicates whether or not using ``Correlation 2" brings an improvement to Variant $A$. We distinguish two cases :
\begin{itemize}
\item[1)] for $j \in \Gamma$, if the total effect index $\ov{$S$}_{u_j}$ requires as much or more evaluations than the first-order index $\underline{S}_{u_j}$. Since the total effect estimator is the same, as a consequence we have $m'_{u_j}=m_{u_j}$ and $c_j >0$.
\item[2)] for $j \in \Gamma$, if the total effect index $\ov{$S$}_{u_j}$ requires less evaluations than the first-order index $\underline{S}_{u_j}$. In this case, if both $m''_{u_j} < m_{u_j}$ and $m'_{u_j} < m_{u_j}$ then $c_j \leq 0$.  
\end{itemize}
{\color{purple}(Lolo) We assume that the effective dimension of the numerator of $\underline{S}_u$ is higher than the one of the numerator of $\ov{$S$}_u$. If this assumption holds, we expect to observe case $2)$ more often than case $1)$ and \eqref{cost.comparison} verifies the following inequality:
\begin{equation}
\sum \limits_{j \in \Gamma} c_j \leq 0 \ .
\label{assumption}
\end{equation}
The validity of this assumption is tested on the numerical examples presented in Section \ref{sec:5}.
%Overall we expect to observe case $2)$ more often than case $1)$. Indeed, the numerator of $\underline{S}_u$ requires to estimate $2d$ dimensional integrals against only $d+1$ dimensional integrals for the numerator of $\ov{$S$}_u$. Hence, it seems reasonable to expect that it will take less points to estimate $\ov{$S$}_u$ than $\underline{S}_u$. 
Furthermore, in case $2)$, we expect the two conditions $m''_{u_j} < m_{u_j}$ and $m'_{u_j} < m_{u_j}$ to usually hold as ``Correlation 2" is shown to perform better for small first-order indices (\textit c.f. \cite{Owen}).}

@@

{\color{purple} (Lolo) To verify the validity of assumption \eqref{assumption}, the sum of the $c_j$ is evaluated for each repetition and barplots of its values are drawn.}

@@

{\color{purple} (Lolo)
\begin{figure}[t]
\caption{Barplots of the $100$ values taken by the sum of the $c_j$. The distribution is bimodal with $60\%$ values equal to $0$.}
\vspace*{0.2cm}
\centering
\includegraphics[width=0.25\textwidth]{sobolg_cj.eps}
\label{cj.gfunc}
\end{figure}
Figure \ref{cj.gfunc} shows barplots of the $100$ values of the sum of the $c_j$. The distribution is bimodal with around $60\%$ of the values equal to $0$ and $40\%$ equal to $512$. As a result, assumption \eqref{assumption} is validated $60\%$ of the times and Variant A.b does not cost more (or slightly more) than Variant A.a.}
\bigskip

\begin{table}[t]
\caption{Averaged estimation errors $\delta_{\underline{S}_u}$ and total number of evaluations for Variant $B$.}
\centering
\begin{tabular}{cccc}
\hline
 input & $\underline{S}_u$ & $\delta_{\underline{S}_u}$ & $r_{\delta_{\underline{S}_u}}$ \\ \hline
 $x_1$ & $0.6043$ &  $0.0005$ & $0$ \\ \hline
 $x_2$ & $0.2360$ &  $0.0010$ & $0$ \\ \hline
 $x_3$ & $0.0286$ &  $0.0018$ & $0.02$ \\ \hline
 $x_4$ & $0.0043$ &  $0.0016$ & $0$    \\ \hline
 $x_5$ & $4.10^{-5}$ & $0.0034$ & $0$  \\ \hline
 $x_6$ & $4.10^{-5}$ & $0.0035$ & $0$  \\ \hline \hline
\multicolumn{4}{l}{Total number of evaluations: $65 \ 536$}\\ \hline 
\end{tabular}
\label{res.gfunc.B}
\end{table}
Table \ref{res.gfunc.B} shows averaged estimation errors $\delta_{\underline{S}_u}$ and total number of evaluations for Variant $B$. The results show that the use of Variant $B$ leads to slightly higher estimation errors than those obtained with Variant $A.a$ or Variant $A.b$. However, the total number of evaluations is {\color{purple}half as large}. As such, this approach remains interesting when one wants to estimate only first-order indices.

@@

{\color{purple} (Lolo)
\begin{figure}[t]
\caption{Barplots of the $100$ values taken by the sum of the $c_j$. $88\%$ of the values are lower or equal to zero. The maximal value equal $3072$.}
\vspace*{0.2cm}
\centering
\includegraphics[width=0.45\textwidth]{bratley_cj.eps}
\label{cj.bratley}
\end{figure}

Figure \ref{cj.bratley} shows barplots of the $100$ values of the sum of the $c_j$. $88\%$ of the values are lower of equal to zero, that is assumption \eqref{assumption} is validated most of the times.}
\bigskip

Table \ref{res.bratley.B} shows averaged estimation errors $\delta_{\underline{S}_u}$ and total number of evaluations for Variant $B$. The estimation errors are lower than those of Variant $A.a$ but higher than those of Variant $A.b$. Failure rates are similar to those of Variant $A.b$. Since the total number of evaluations is close to the one of Variant $A.b$ at the exception of input $x_4$. As a conclusion, Variant $B$ does not bring much improvement for this example.
\begin{table}[!ht]
\caption{Averaged estimation errors $\delta_{\underline{S}_u}$ and total number of evaluations for Variant $B$.}
\centering
\begin{tabular}{cccc}
\hline
 input & $\underline{S}_u$ & $\delta_{\underline{S}_u}$ & $r_{\delta_{\underline{S}_u}}$ \\ \hline
 $x_1$ & $0.6529$ &  $0.0004$ & $0$ \\ \hline
 $x_2$ & $0.1791$ &  $0.0006$ & $0$ \\ \hline
 $x_3$ & $0.0370$ &  $0.0007$ & $0$ \\ \hline
 $x_4$ & $0.0133$ &  $0.0037$ & $0.25$    \\ \hline
 $x_5$ & $0.0015$ & $0.0023$ & $0$  \\ \hline
 $x_6$ & $0.0015$ & $0.0025$ & $0$  \\ \hline \hline
\multicolumn{4}{l}{Total number of evaluations: $65 \ 536$}\\ \hline 
\end{tabular}
\label{res.bratley.B}
\end{table}
\bigskip

@@

(Lolo) As an application, we will study the wing weight function introduced by Forrester \textit{et al.} \cite{Forrester} and defined as follows:
\begin{align*}
f(\vx)=0.036 x_1^{0.758} & x_2^{0.0035} \left(\frac{x_3}{\cos(x_4)^2}\right)^{0.6} x_5^{0.006} x_6^{0.04}\times \\
 & \times\left(\frac{100 x_7}{\cos(x_4)}\right)^{-0.3} (x_8 x_9)^{0.49} + x_1 x_{10}
\end{align*}
Table \ref{wing_inputs_table} gives the range of variation of each input and their physical representation.  All inputs are independent and uniformly distributed in their respective ranges.
\begin{table}[!ht]
\caption{Inputs and their ranges of variation. All inputs are independent and uniformly distributed in their respective ranges.}
\centering
\begin{tabular}{ccc}
\hline
 inputs & range & description \\ \hline
$x_1$ & $[150, 200]$ & wing area (ft$^2$) \\
$x_2$ & $[220, 300]$ & weight of fuel in the wing (lb) \\
$x_3$ & $[6, 10]$ & aspect ratio \\
$x_4$ & $[-10, 10]$ & quarter-chord sweep (degrees) \\
$x_5$ & $[16, 45]$ & dynamic pressure at cruise (lb/ft$^2$) \\
$x_6$ & $[0.5, 1]$ & taper ratio \\
$x_7$ & $[0.08, 0.18]$ & aerofoil thickness to chord ratio \\
$x_8$ & $[2.5, 6]$ & ultimate load factor \\
$x_9$ & $[1700, 2500]$ & flight design gross weight (lb) \\
$x_{10}$ & $[0.025, 0.08]$ & paint weight (lb/ft$^2$) \\
\hline
\end{tabular}
\label{wing_inputs_table}
\end{table}

>>>>

Then, as an alternative to the common Sobol' indices estimators (\ref{common.sobol.est}), we can define the following two estimators with their respective error bounds:
\begin{gather}
\begin{aligned}
\widehat{\underline{S}}_u & = \frac{1}{2}\left(\min\Big{(}\max_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \underline{S}_u(\vI),1\Big{)} + \max\Big{(}\min_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \underline{S}_u(\vI),0\Big{)} \right) \\
\varepsilon_{\widehat{\underline{S}}_u} & = \frac{1}{2}\left(\min\Big{(}\max_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \underline{S}_u(\vI),1\Big{)} - \max\Big{(}\min_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \underline{S}_u(\vI),0\Big{)} \right)
\end{aligned}
\label{formula_undersu}
\end{gather}
and,
\begin{gather}
\begin{aligned}
\widehat{\overline{S}}_u & = \frac{1}{2}\left(\min\Big{(}\max_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \overline{S}_u(\vI),1\Big{)} + \max\Big{(}\min_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \overline{S}_u(\vI),0\Big{)} \right) \\
\varepsilon_{\widehat{\overline{S}}_u} & = \frac{1}{2}\left(\min\Big{(}\max_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \overline{S}_u(\vI),1\Big{)} - \max\Big{(}\min_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \overline{S}_u(\vI),0\Big{)} \right)
\end{aligned}
\label{formula_oversu}
\end{gather}
Because numerator and denominator are both known to be positive, maximizing $\underline{S}_u(\vI)$ (resp. $\overline{S}_u(\vI)$) is done through maximizing the numerator $I_1$ (resp. $I_2$) and minimizing the denominator $I_3-I_4^2$. Analogously, to minimize $\underline{S}_u(\vI)$ (resp. $\overline{S}_u(\vI)$) one minimizes the numerator $I_1$ (resp. $I_2$) and maximizes the denominator $I_3-I_4^2$. As an example, Figure \ref{fig:1} illustrates the region of possible values of $\underline{S}_2(\vI)$ given the true value of $I_1$ for the test function of Bratley \textit{et al.} \cite{Bratley}. This function is further described in Section \ref{sec:5}. 
\begin{figure}[t]
\caption{The delimited region on the figure represents the values $\underline{S}_2$ in $\vI\in B_{(0,0,0.05,0.1)}(\widehat{\vI})$ for the Bratley \textit{et al.} function. There, $\underline{S}_2^{\min}=\max\Big{(}\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_2(\vI),0\Big{)}$ and $\underline{S}_2^{\max}=\min\Big{(}\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_2(\vI),1\Big{)}$, and $\widehat{\underline{S}}_2=(\underline{S}_2^{\min}+\underline{S}_2^{\max})/2$.}
\centering
\includegraphics[width=.5\textwidth]{estimator_3d_small.eps}
\label{fig:1}       % Give a unique label
\end{figure}

@@

If the stopping criterion is satisfied, the algorithm stops and Sobol' estimates are returned. Otherwise, $m$ is incremented by one to perform a new estimation. 
\begin{algorithm}[t]
\caption{Sequential estimation of Sobol' indices}
\begin{algorithmic}[1]
\vspace*{0.2cm}
\State choose $\epsilon >0$
\State set: $m \leftarrow \ell_*+r$
\State $bool \leftarrow false$
\While {$! bool$}
\State $\mathcal{P}_m \leftarrow \mathcal{P}_{m-1} \cup B_m$

@@

Assume that the number of small first-order indices is known and equals $\gamma$. We denote by $u_1,\dots,u_{\gamma}$ the indices of the corresponding inputs and $\Gamma = \{1,\dots,\gamma\}$. The cost of Variant $A$ including ``Correlation 2" becomes, 
\begin{equation}
\sum \limits_{j \in \Gamma} 2^{m''_{u_j}} + \sum \limits_{j \in \Gamma} 2^{m'_{u_j}} + \sum \limits_{j \in \mathcal{D}\setminus{\Gamma}} 2^{m_{u_j}} + 2 \times 2^{m^\star},
\label{cost.improvement}
\end{equation}
where: %$m'_{u_j}\leq m^{\star}$, $\ m_{u_j} \leq m^{\star}$, and: 
\begin{itemize}
\item[$\bullet$] for $j\in \Gamma$, $2^{m''_{u_j}}$ is the number of evaluations \\ $f\left(\vz_{i,u_j}:\vx_{i,-u_j}\right)$ to estimate $\underline{S}_{u_j}$,
\item[$\bullet$] for $j\in \Gamma$, $2^{m'_{u_j}}$ is the number of evaluations \\ $f\left(\vx_{i,u_j}:{\vx'}_{i,-u_j}\right)$ to estimate both $\underline{S}_{u_j}$ and  $\overline{S}_{u_j}$,
\item[$\bullet$] likewise, for $j\in \mathcal{D}\setminus{\Gamma}$, $ 2^{m_{u_j}}$ is the number of evaluations $f\left(\vx_{i,u_j}:{\vx'}_{i,-u_j}\right)$ to estimate both $\underline{S}_{u_j}$ and  $\overline{S}_{u_j}$,
\item[$\bullet$] $2 \times 2^{m^{\star}}$ is the number of evaluations $f\left(\vx_{i}\right)$ and $f\left({\vx'}_{i}\right)$ used in the estimation of each first-order and total effect index.
\end{itemize}
We recall the cost of Variant $A$ without  ``Correlation 2",
\begin{equation}
\sum \limits_{j \in \Gamma} 2^{m_{u_j}} + \sum \limits_{j \in \mathcal{D}\setminus{\Gamma}} 2^{m_{u_j}} + 2 \times 2^{m^{\star}}. 
%\qquad m_{u_j} \leq m^{\star}.
\label{cost.non.improvement}
\end{equation}
The difference (\ref{cost.improvement}) $-$ (\ref{cost.non.improvement}) equals:
\begin{equation}
 \sum \limits_{j \in \Gamma} 2^{m_{u_j}} \left(2^{m''_{u_j}-m_{u_j}}  + 2^{m'_{u_j}-m_{u_j}} - 1 \right) = \sum \limits_{j \in \Gamma} c_j.
\label{cost.comparison}
\end{equation}
{\color{purple} (Lolo) The sign of \eqref{cost.comparison}} indicates whether or not using ``Correlation 2" brings an improvement to Variant $A$. We distinguish two cases :
\begin{itemize}
\item[1)] for $j \in \Gamma$, if the total effect index $\ov{$S$}_{u_j}$ requires as much or more evaluations than the first-order index $\underline{S}_{u_j}$. Since the total effect estimator is the same, as a consequence we have $m'_{u_j}=m_{u_j}$ and $c_j >0$.
\item[2)] for $j \in \Gamma$, if the total effect index $\ov{$S$}_{u_j}$ requires less evaluations than the first-order index $\underline{S}_{u_j}$. In this case, if both $m''_{u_j} < m_{u_j}$ and $m'_{u_j} < m_{u_j}$ then $c_j \leq 0$.  
\end{itemize}
{\color{purple}(Lolo) We assume that the effective dimension of the numerator of $\underline{S}_u$ is higher than the one of the numerator of $\ov{$S$}_u$. This assumption is tested on the numerical examples presented in Section \ref{sec:5.1} by comparing the number of evaluations required by the two numerators.

If this assumption holds, we expect to observe case $2)$ more often than case $1)$. Furthermore, in case $2)$, we expect the two conditions $m''_{u_j} < m_{u_j}$ and $m'_{u_j} < m_{u_j}$ to usually hold as ``Correlation 2" is shown to perform better for small first-order indices (\textit c.f. \cite{Owen}).}
\bigskip

@@

%{\color{purple} (Lolo) To test if the effective dimension of the numerator of $\underline{S}_u$ is higher than the one of the numerator of $\ov{$S$}_u$,

%To verify the validity of assumption \eqref{assumption}, the sum of the $c_j$ is evaluated for each repetition and barplots of its values are drawn.}

@@

{\color{purple}(Lolo) Table \ref{comparison.gfunc} shows the average number of evaluations performed in Variant $A.a$ to estimate $I_1$, the numerator of $\underline{S}_u$, and $I_2$, the numerator of $\ov{$S$}_u$. The column $I_2 > I_1$ indicates the number of times where $I_2$ required more evaluations than $I_1$. We observe that $I_2$ never requires more evaluations than $I_1$. This seems to indicate that the effective dimension of $I_1$ is higher than $I_2$ for this example.
\begin{table}[t]
\caption{Number of evaluations evaluations performed to estimate $I_1$ and $I_2$ in Variant $A.a$. $N$ is the number of times among the $100$ repeats where $I_2$ required more evaluations than $I_1$}
\centering
\begin{tabular}{cccc}
\hline
 input & $I_1$ & $I_2$ & $I_2 > I_1$ \\ \hline
 $x_1$ & $32768$ & $32768$ & $0$ \\   \hline
 $x_2$ & $16384$ & $16384$ & $0$ \\  \hline
 $x_3$ & $4096$ & $2048$ & $0$ \\  \hline
 $x_4$ & $830$ & $512$ & $0$ \\  \hline
 $x_5$ & $512$ & $512$ & $0$ \\  \hline
 $x_6$ & $512$ & $512$ & $0$ \\  \hline
\end{tabular}
\label{comparison.gfunc}
\end{table}}
\bigskip

Table \ref{res.gfunc.B} shows averaged estimation errors $\delta_{\underline{S}_u}$ and total number of evaluations for Variant $B$. The results show that the use of Variant $B$ leads to slightly higher estimation errors than those obtained with Variant $A.a$ or Variant $A.b$. However, the total number of evaluations is {\color{purple}half as large}. As such, this approach remains interesting when one wants to estimate only first-order indices.
\begin{table}[t]
\caption{Averaged estimation errors $\delta_{\underline{S}_u}$ and total number of evaluations for Variant $B$.}
\centering
\begin{tabular}{cccc}
\hline
 input & $\underline{S}_u$ & $\delta_{\underline{S}_u}$ & $r_{\delta_{\underline{S}_u}}$ \\ \hline
 $x_1$ & $0.6043$ &  $0.0005$ & $0$ \\ \hline
 $x_2$ & $0.2360$ &  $0.0010$ & $0$ \\ \hline
 $x_3$ & $0.0286$ &  $0.0018$ & $0.02$ \\ \hline
 $x_4$ & $0.0043$ &  $0.0016$ & $0$    \\ \hline
 $x_5$ & $4.10^{-5}$ & $0.0034$ & $0$  \\ \hline
 $x_6$ & $4.10^{-5}$ & $0.0035$ & $0$  \\ \hline \hline
\multicolumn{4}{l}{Total number of evaluations: $65 \ 536$}\\ \hline 
\end{tabular}
\label{res.gfunc.B}
\end{table}

@@

{\color{purple}(Lolo) Table \ref{comparison.bratley} shows the average number of evaluations performed in Variant $A.a$ to estimate $I_1$, the numerator of $\underline{S}_u$, and $I_2$, the numerator of $\ov{$S$}_u$. The column $I_2 > I_1$ indicates the number of times among the $100$ repeats where $I_2$ required more evaluations than $I_1$. 
\begin{table}[t]
\caption{Number of evaluations evaluations performed to estimate $I_1$ and $I_2$ in Variant $A.a$. $N$ is the number of times where $I_2$ required more evaluations than $I_1$}
\centering
\begin{tabular}{cccc}
\hline
 input & $I_1$ & $I_2$ & $I_2 > I_1$ \\ \hline
 $x_1$ & $16876$ & $16384$ & $0$ \\  \hline
 $x_2$ & $8520$ & $8192$ & $0$ \\  \hline
 $x_3$ & $4096$ & $2786$ & $0$ \\  \hline
 $x_4$ & $3794$ & $1096$ & $4$ \\  \hline
 $x_5$ & $635$ & $512$ & $0$ \\  \hline
 $x_6$ & $712$ & $512$ & $0$ \\ 
\hline 
\end{tabular}
\label{comparison.bratley}
\end{table}
\begin{table}[t]
\caption{Averaged estimation errors $\delta_{\underline{S}_u}$ and total number of evaluations for Variant $B$.}
\centering
\begin{tabular}{cccc}
\hline
 input & $\underline{S}_u$ & $\delta_{\underline{S}_u}$ & $r_{\delta_{\underline{S}_u}}$ \\ \hline
 $x_1$ & $0.6529$ &  $0.0004$ & $0$ \\ \hline
 $x_2$ & $0.1791$ &  $0.0006$ & $0$ \\ \hline
 $x_3$ & $0.0370$ &  $0.0007$ & $0$ \\ \hline
 $x_4$ & $0.0133$ &  $0.0037$ & $0.25$    \\ \hline
 $x_5$ & $0.0015$ & $0.0023$ & $0$  \\ \hline
 $x_6$ & $0.0015$ & $0.0025$ & $0$  \\ \hline \hline
\multicolumn{4}{l}{Total number of evaluations: $65 \ 536$}\\ \hline 
\end{tabular}
\label{res.bratley.B}
\end{table}
We observe that $I_2$ almost never requires more evaluations than $I_1$. This seems to indicate that the effective dimension of $I_1$ is also higher than $I_2$ for this example.}

Table \ref{res.bratley.B} shows averaged estimation errors $\delta_{\underline{S}_u}$ and total number of evaluations for Variant $B$. The estimation errors are lower than those of Variant $A.a$ but higher than those of Variant $A.b$. Failure rates are similar to those of Variant $A.b$. Since the total number of evaluations is close to the one of Variant $A.b$ at the exception of input $x_4$. As a conclusion, Variant $B$ does not bring much improvement for this example.
\bigskip

@@

(Lolo) As an application, we will study the wing weight function introduced by Forrester \textit{et al.} \cite{Forrester} and defined as follows:
\begin{align*}
f(\vx)=0.036 x_1^{0.758} & x_2^{0.0035} \left(\frac{x_3}{\cos(x_4)^2}\right)^{0.6} x_5^{0.006} x_6^{0.04}\times \\
 & \times\left(\frac{100 x_7}{\cos(x_4)}\right)^{-0.3} (x_8 x_9)^{0.49} + x_1 x_{10}
\end{align*}
Table \ref{wing_inputs_table} gives the range of variation of each input and their physical representation.  All inputs are uniformly distributed in their respective ranges. To illustrate the performance of our procedure, five additional inert inputs $x_{11}$, $\dots$, $x_{15}$ are added which serve only to add ``noise'' to the sensitivity analysis. The inert inputs are all uniformly distributed in $[0,1]$.
\begin{table}[!ht]
\caption{Inputs and their ranges of variation. All inputs are uniformly distributed in their respective ranges.}
\centering
\begin{tabular}{ccc}
\hline
 inputs & range & description \\ \hline
$x_1$ & $[150, 200]$ & wing area (ft$^2$) \\
$x_2$ & $[220, 300]$ & weight of fuel in the wing (lb) \\
$x_3$ & $[6, 10]$ & aspect ratio \\
$x_4$ & $[-10, 10]$ & quarter-chord sweep (degrees) \\
$x_5$ & $[16, 45]$ & dynamic pressure at cruise (lb/ft$^2$) \\
$x_6$ & $[0.5, 1]$ & taper ratio \\
$x_7$ & $[0.08, 0.18]$ & aerofoil thickness to chord ratio \\
$x_8$ & $[2.5, 6]$ & ultimate load factor \\
$x_9$ & $[1700, 2500]$ & flight design gross weight (lb) \\
$x_{10}$ & $[0.025, 0.08]$ & paint weight (lb/ft$^2$) \\
$x_{11},\dots,x_{15}$ & $[0,1]$ & ``noise'' \\
\hline
\end{tabular}
\label{wing_inputs_table}
\end{table}

The motivation of this application is to test if our procedure capture the same set of influent inputs $(x_1,x_3,x_7,x_8,x_9)$ selected by the analysis of Forrester \textit{et al.}.

A second motivation is to compare the performance of each variant ($A.a$, $A.b$ and $B$) on a function where true values of Sobol' indices cannot be computed. The comparison is based on averaged Sobol' estimates and averaged total number of evaluations over $100$ repetitions.
\bigskip

Tables \ref{res.wing.Aa}, \ref{res.wing.Ab} show the results obtained with Variant $A.a$ and  Variant $A.b$. Both variants capture well the presence of inert inputs. Variant A.b is more expansive but validates the property that first-order indices are lower or equal to total-effect indices. At the opposite, Variant A.a fails to guarantee this property for inputs with small main effects: $x_2$, $x_4$, $x_5$, $x_6$. This highlights once again the efficiency of ``Correlation 2''. The boxplots represented in Figure \ref{boxplots.wing} emphasize the latter observation, Variant $A.b$ provides less variance in the estimates.

\begin{table}[!ht]
\caption{Averaged values of $\widehat{\underline{S}}_u$, ${\widehat{\overline{S}}_u}$, and total number of evaluations of Variant $A.a$.}
\centering
\begin{tabular}{ccc}
\hline
 input & $\widehat{\underline{S}}_u$ & $\widehat{\overline{S}}_u$ \\ \hline
 $x_1$ & $0.1245$ & $0.1279$  \\ \hline
 $x_2$ & $0.0001$ & $< 10^{-4}$  \\ \hline
 $x_3$ & $0.2203$ & $0.2261$  \\ \hline
 $x_4$ & $0.0022$ & $0.0006$  \\ \hline
 $x_5$ & $0.0011$ & $0.0001$  \\ \hline
 $x_6$ & $0.0037$ & $0.0024$  \\ \hline 
 $x_7$ & $0.1410$ & $0.1452$  \\ \hline
 $x_8$ & $0.4116$ & $0.4196$  \\ \hline
 $x_9$ & $0.0851$ & $0.0877$  \\ \hline
 $x_{10}$ & $0.0038$ & $0.0043$  \\ \hline
 $x_{11},\dots,x_{15}$ & $0$ & $0$  \\ \hline
\hline
\multicolumn{3}{l}{Total number of evaluations: $87 \ 844$} \\ \hline 
\end{tabular}
\label{res.wing.Aa}
\end{table}
\begin{table}[!ht]
\caption{Averaged values of $\widehat{\underline{S}}_u$, ${\widehat{\overline{S}}_u}$ and total number of evaluations of Variant $A.b$.}
 \centering
\begin{tabular}{ccc}
\hline
  input & $\widehat{\underline{S}}_u$ & $\widehat{\overline{S}}_u$ \\ \hline
 $x_1$ & $0.1245$ & $0.1279$  \\ \hline
 $x_2$ & $< 10^{-4}$ & $< 10^{-4}$  \\ \hline
 $x_3$ & $0.2203$ & $0.2261$  \\ \hline
 $x_4$ & $0.0006$ & $0.0006$  \\ \hline
 $x_5$ & $0.0001$ & $0.0001$  \\ \hline
 $x_6$ & $0.0023$ & $0.0024$  \\ \hline 
 $x_7$ & $0.1410$ & $0.1452$  \\ \hline
 $x_8$ & $0.4116$ & $0.4196$  \\ \hline
 $x_9$ & $0.0851$ & $0.0877$  \\ \hline
 $x_{10}$ & $0.0043$ & $0.0043$  \\ \hline
 $x_{11},\dots,x_{15}$ & $0$ & $0$  \\ \hline
\hline
\multicolumn{3}{l}{Total number of evaluations: $93 \ 881$} \\ \hline 
\end{tabular}
\label{res.wing.Ab}
\end{table}

\begin{figure}[!ht]
\caption{Boxplots of first-order indices $\underline{S}_u$ for inputs $x_2,x_4,x_5,x_6,x_{10}$ obtained with both Variant $A.a$ and Variant $A.b$.}
\vspace*{0.2cm}
\centering
\includegraphics[width=0.45\textwidth]{wingweight_box.eps}
\label{boxplots.wing}
\end{figure}

Tables \ref{res.wing.B} show the results obtained with Variant $B$. Variant $B$ does not capture the presence of the inert inputs $x_{11}$, $\dots$, $x_{15}$. Their estimated main effects are confused with those of inputs $x_4$, $x_5$, $x_6$,$x_9$ and $x_{10}$.  However, the drawback of overestimating small first-order indices is balanced by the improvement in terms of number of evaluations.
